% Created 2018-01-13 Sat 11:45
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{booktabs}\usepackage{multirow}
\author{Daniel Molina Cabrera <dmolina@decsai.ugr.es}
\date{\today}
\title{Comparative with IHDELS and IHSHADELS (and versions)}
\hypersetup{
 pdfauthor={Daniel Molina Cabrera <dmolina@decsai.ugr.es},
 pdftitle={Comparative with IHDELS and IHSHADELS (and versions)},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 25.1.1 (Org mode 9.1.2)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents


\section{Original version IHDELS-CEC2015}
\label{sec:org94939ca}


\subsection{Comparison against MOS}
\label{sec:org4487420}

\input{table_original_mos.tex}

\subsection{Conclusions}
\label{sec:org8a2809b}

\begin{itemize}
\item MOS improve in 12 of 15 functions.
\item IHDELS is not competitive.
\end{itemize}


\section{IHDELS-CEC2015 vs IHDELS-Restart}
\label{sec:org3874841}

\subsection{Differences}
\label{sec:org1e63b23}

\begin{itemize}
\item Changed the selection of LS method.

\item Changed the restart, the original did not applied restart in many function,
and never improve.
\end{itemize}

\subsection{Comparison}
\label{sec:org6726dc8}

\input{table_original.tex}

\begin{itemize}
\item Improve in 10 of 15 functions.
\item Improve specially in more difficult problems.
\end{itemize}

\subsection{Comparison against MOS}
\label{sec:org6a26c8a}

\input{table_restart_mos.tex}

\begin{itemize}
\item Now IHDELS\(_{\text{restart}}\) improve in 7 of 15 functions.
\item Improve specially in more difficult ones.
\item In several functions: F11, F13 the improvement is several order of magnitud.
\end{itemize}

\section{New proposal:  IHDELS vs IHSHADELS}
\label{sec:orgb4c976e}
\end{document}